
\section{Conclusions}


\begin{frame}
  \frametitle{blah}

  blah blah blah

\end{frame}

 
\begin{frame}
  \frametitle{Bibliography}

 \begin{thebibliography}{1}
 
 \bibitem{Dinsdale}
   E. Dinsdale, F. Rohwer.
   \newblock Fish or Germs? Microbial Dynamics Associated with Changing Trophic Structures on Coral Reefs.
   \newblock \emph{Coral Reefs: An Ecosystem in Transition}, Springer Science and Business, pp 231-240, 2011.

 \bibitem{doi:10.1137/S0036144500378302}
   D.~Higham.
   \newblock An algorithmic introduction to numerical simulation of stochastic
   differential equations.
   \newblock {\em SIAM Review}, 43(3):525--546, 2001.
 \bibitem{Hastings}
   X.~Li, H.~Wang, Z.~Zhang, A.~Hastings.
   \newblock Mathematical analysis of coral reef models.
   \newblock {\em Journal of Mathematical Analysis and Applications}, 416:352--373, 2014.

  \bibitem{McClanahan}
    McClanahan
    \newblock A coral reef ecosystem-fisheries model: impacts of fishing intensity and catch selection on reef structure and processes.
    \newblock {\em Ecological Modelling}, 80:1-19, 1995.

  \bibitem{Mumby}
    Mumby, Hastings, Edwards.
    \newblock Thresholds and the resilience of Caribbean Coral Reefs.
    \newblock {\em Nature}, 2007.
  \end{thebibliography}
  
\end{frame}

\begin{frame}
  \frametitle{Acknowledgments}
  
  We would like to thank the following for their support and funding: 
  
 \begin{itemize}
 \item Dr. Joel Foisy, SUNY Potsdam
 \item National Security Agency (H98230-14-1-0141)
 \item National Science Foundation (DSM-1262737)
 \item Universidad Aut\'onoma del Estado de Hidalgo
 \end{itemize}
\end{frame}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "Presentation2"
%%% End:
